---
title: ""
author: ""
date: ""
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 3
    smooth_scroll: false
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(data.table)
library(ggplot2)
library(rtracklayer)
library(knitr)
#
library(TxDb.Mmusculus.UCSC.mm10.knownGene)
library(org.Mm.eg.db)
library(ChIPseeker)
#
txdb <- TxDb.Mmusculus.UCSC.mm10.knownGene
#
options(ChIPseeker.ignore_1st_exon = TRUE)
options(ChIPseeker.ignore_1st_intron = TRUE)
options(ChIPseeker.ignore_downstream = TRUE)
options(ChIPseeker.ignore_promoter_subcategory = TRUE)
#
library(pacman)
pacman::p_load(argparse,tidyverse,rtracklayer,GenomicRanges,LOLA,highcharter)
#
signif.num <- function(x) {
  symnum(x, corr = FALSE, na = FALSE, legend = FALSE,
         cutpoints = c(0, 0.0001, 0.001, 0.01, 0.05, 1), 
         symbols = c("****", "***", "**", "*", "ns"))
}
```

# TKO vs QKO {.tabset}

## Scatterplot {.tabset}

### Removing cluster of bins at 0

Removing the cluster where K36me2 is 0 for both conditions does not result in any viable clusters.
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("~/Documents/10T_K36me_Manuscript/images/TKO.NSD3.K36me2/removed_cluster_zero", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

### Subsetting bins 

Instead, we can focus on bins that pass a specific threshold. These bins would be located within the red box below, indicating K36me2 deposited by NSD3 that is lost in QKO.
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("~/Documents/10T_K36me_Manuscript/images/TKO.NSD3.K36me2", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

## Distribution
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("~/Documents/10T_K36me_Manuscript/images/TKO.NSD3.K36me2/distribution", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

## Enrichment analysis {.tabset}

### Complete
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
#
load(file="~/Documents/10T_K36me_Manuscript/data/Residual_K36me2/enrichment_plots/NSD3_deposited_K36me2.whole.TKO.RData")
#
res %>% mutate(reg = sub('.bed', '', filename),
                        sig = as.character(signif.num(qValue)),
                        q = case_when(qValue > 0 ~ qValue, T ~ min(qValue[qValue > 0])),
                        q = -log10(q),
                    info = sprintf('Odds ratio: %.3g <br>FDR: %.3g<br>Overlap: %d<br>|Annotation|: %d', oddsRatio, qValue, support, size),
                        oddsRatio = case_when(oddsRatio > 0 ~ oddsRatio, T ~ min(oddsRatio[oddsRatio > 0]))) %>%
  hchart('scatter', hcaes(x = oddsRatio, y = q, size = support,
                          group = reg), maxSize = '10%') %>%
  hc_xAxis( title = list(text = 'Odds ratio'), type = 'logarithmic') %>%
  hc_yAxis(title = list(text = '-log10(padj)')) %>%
  hc_tooltip(pointFormatter = JS("function() {
      return this.options.info;
  }")) %>%
  hc_chart(zoomType = 'xy')
#
```

### Genic
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
#
load(file="~/Documents/10T_K36me_Manuscript/data/Residual_K36me2/enrichment_plots/NSD3_deposited_K36me2.genic.TKO.RData")
#
res %>% mutate(reg = sub('.bed', '', filename),
                        sig = as.character(signif.num(qValue)),
                        q = case_when(qValue > 0 ~ qValue, T ~ min(qValue[qValue > 0])),
                        q = -log10(q),
                    info = sprintf('Odds ratio: %.3g <br>FDR: %.3g<br>Overlap: %d<br>|Annotation|: %d', oddsRatio, qValue, support, size),
                        oddsRatio = case_when(oddsRatio > 0 ~ oddsRatio, T ~ min(oddsRatio[oddsRatio > 0]))) %>%
  hchart('scatter', hcaes(x = oddsRatio, y = q, size = support,
                          group = reg), maxSize = '10%') %>%
  hc_xAxis( title = list(text = 'Odds ratio'), type = 'logarithmic') %>%
  hc_yAxis(title = list(text = '-log10(padj)')) %>%
  hc_tooltip(pointFormatter = JS("function() {
      return this.options.info;
  }")) %>%
  hc_chart(zoomType = 'xy')
#
```

### Intergenic
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
#
load(file="~/Documents/10T_K36me_Manuscript/data/Residual_K36me2/enrichment_plots/NSD3_deposited_K36me2.igr.TKO.RData")
#
res %>% mutate(reg = sub('.bed', '', filename),
                        sig = as.character(signif.num(qValue)),
                        q = case_when(qValue > 0 ~ qValue, T ~ min(qValue[qValue > 0])),
                        q = -log10(q),
                    info = sprintf('Odds ratio: %.3g <br>FDR: %.3g<br>Overlap: %d<br>|Annotation|: %d', oddsRatio, qValue, support, size),
                        oddsRatio = case_when(oddsRatio > 0 ~ oddsRatio, T ~ min(oddsRatio[oddsRatio > 0]))) %>%
  hchart('scatter', hcaes(x = oddsRatio, y = q, size = support,
                          group = reg), maxSize = '10%') %>%
  hc_xAxis( title = list(text = 'Odds ratio'), type = 'logarithmic') %>%
  hc_yAxis(title = list(text = '-log10(padj)')) %>%
  hc_tooltip(pointFormatter = JS("function() {
      return this.options.info;
  }")) %>%
  hc_chart(zoomType = 'xy')
#
```

---

## Depletion analysis {.tabset}

### Complete
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
#
load(file="~/Documents/10T_K36me_Manuscript/data/Residual_K36me2/enrichment_plots/NSD3_deposited_K36me2.depleted.whole.TKO.RData")
#
res.dep %>% mutate(reg = sub('.bed', '', filename),
                        sig = as.character(signif.num(qValue)),
                        q = case_when(qValue > 0 ~ qValue, T ~ min(qValue[qValue > 0])),
                        q = -log10(q),
                    info = sprintf('Odds ratio: %.3g <br>FDR: %.3g<br>Overlap: %d<br>|Annotation|: %d', oddsRatio, qValue, support, size),
                        oddsRatio = case_when(oddsRatio > 0 ~ oddsRatio, T ~ min(oddsRatio[oddsRatio > 0]))) %>%
  hchart('scatter', hcaes(x = oddsRatio, y = q, size = support,
                          group = reg), maxSize = '10%') %>%
  hc_xAxis( title = list(text = 'Odds ratio'), type = 'logarithmic') %>%
  hc_yAxis(title = list(text = '-log10(padj)')) %>%
  hc_tooltip(pointFormatter = JS("function() {
      return this.options.info;
  }")) %>%
  hc_chart(zoomType = 'xy')
#
```

### Genic
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
#
load(file="~/Documents/10T_K36me_Manuscript/data/Residual_K36me2/enrichment_plots/NSD3_deposited_K36me2.depleted.genic.TKO.RData")
#
res.dep %>% mutate(reg = sub('.bed', '', filename),
                        sig = as.character(signif.num(qValue)),
                        q = case_when(qValue > 0 ~ qValue, T ~ min(qValue[qValue > 0])),
                        q = -log10(q),
                    info = sprintf('Odds ratio: %.3g <br>FDR: %.3g<br>Overlap: %d<br>|Annotation|: %d', oddsRatio, qValue, support, size),
                        oddsRatio = case_when(oddsRatio > 0 ~ oddsRatio, T ~ min(oddsRatio[oddsRatio > 0]))) %>%
  hchart('scatter', hcaes(x = oddsRatio, y = q, size = support,
                          group = reg), maxSize = '10%') %>%
  hc_xAxis( title = list(text = 'Odds ratio'), type = 'logarithmic') %>%
  hc_yAxis(title = list(text = '-log10(padj)')) %>%
  hc_tooltip(pointFormatter = JS("function() {
      return this.options.info;
  }")) %>%
  hc_chart(zoomType = 'xy')
#
```

### Intergenic
```{r,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
#
load(file="~/Documents/10T_K36me_Manuscript/data/Residual_K36me2/enrichment_plots/NSD3_deposited_K36me2.depleted.igr.TKO.RData")
#
res.dep %>% mutate(reg = sub('.bed', '', filename),
                        sig = as.character(signif.num(qValue)),
                        q = case_when(qValue > 0 ~ qValue, T ~ min(qValue[qValue > 0])),
                        q = -log10(q),
                    info = sprintf('Odds ratio: %.3g <br>FDR: %.3g<br>Overlap: %d<br>|Annotation|: %d', oddsRatio, qValue, support, size),
                        oddsRatio = case_when(oddsRatio > 0 ~ oddsRatio, T ~ min(oddsRatio[oddsRatio > 0]))) %>%
  hchart('scatter', hcaes(x = oddsRatio, y = q, size = support,
                          group = reg), maxSize = '10%') %>%
  hc_xAxis( title = list(text = 'Odds ratio'), type = 'logarithmic') %>%
  hc_yAxis(title = list(text = '-log10(padj)')) %>%
  hc_tooltip(pointFormatter = JS("function() {
      return this.options.info;
  }")) %>%
  hc_chart(zoomType = 'xy')
#
```
